The Feasibility of Stylometry as a Service

### 2013-12-08 paper/paper.tex
Added modifiability paragraph.

@@

>>>>

The stylometric web service should be interoperability with the modern
web architecture.  Specifically, it should be a service based on
Representational State Transfer (REST)\cite{Fielding2000}.  REST web
services define a framework that is client-server, has a uniform
interface based on HTTP verbs, and supports a layered architecture.
These features are in-line with the goals of a stylometric web
service.  Using a REST service, the client software can be a web
browser, which is nearly ubiqiteious on mobile devices.

@@

One of the goals of the service is provide a platform for stylometric
research.  In this sense in must be modifable to accomodate different
kinds of experiments including ones not currently anticipated.
Software engineering best pratices are applicable here mainly having
well abstracted interfaces and modular components.  As a RESTful web
service, each endpoint should have a concise application programming
interface (API) for a given feature set.  For example, there should be
a stylometry endpoint that can process text and return features.
Other services, such as an adversarial stylometry service, should use
the stylometric service via its REST API.

A web service has a distinct advantage here over the modifiability of
the desktop software.  One can deploy an updated version of the
software by pushing the update to servers and instantly clients will
have the new version.  As a research platform, this is a very valuable
feature.  For example, split testing or A/B testing, is much easier to
control and manage with a web service than packaged software.
